\documentclass[margin,line]{CV}

\usepackage{enumitem}
\usepackage[colorlinks = true,
linkcolor = blue,
urlcolor  = blue,
citecolor = blue,
anchorcolor = blue]{hyperref}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Eric Nunes \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
699 S. Mill Avenue            & {\it Voice:}  (315) 439-3089\\                    
Arizona State University & {\it E-mail:}  \href{mailto:enunes1@asu.edu}{\bf enunes1@asu.edu}\\       
Tempe, AZ  85281 USA  & {\it website:} \href{https://efnunes.github.io/}{\bf efnunes.github.io} \\     
\end{tabular}


%\section{\sc Research Interests}
%Artificial Intelligence, Machine learning and statistical methods for large datasets, data-driven cyber security, security informatics.

\section{\sc Education}
\href{http://www.asu.edu/}{\bf Arizona State University}, Tempe, Arizona USA\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. Computer Engineering (GPA: 4.0/4.0), August 2014 - Present
\begin{list2}
\vspace*{.05in}
\item Dissertation Topic:  ``Reasoning about Cyber Threat Actors'' 
%\item Dissertation Topic:  ``Hierarchical Models for Multiple Ratings
%  in Performance-Based\\ \hspace*{1.23in} Student Assessments.'' 
\item Advisor:  Paulo Shakarian
\item Ph.D. Candidate - May 2017
\end{list2}
\end{list1}

\href{http://www.syr.edu/}{\bf Syracuse University}, Syracuse, New York USA\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] M.S. Electrical Engineering,  May 2012
\end{list1}

\href{http://archive.mu.ac.in/}{\bf University of Mumbai}, Mumbai, India\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] B.S. Electronics and Telecommunication,  June 2010
\end{list1}


\section{\sc Honors and Awards} 
\begin{itemize}[leftmargin =*]

\item IEEE/ACM International Symposium on Foundations of Open Source Intelligence and Security Informatics (FOSINT-SI), 2016 \textbf{Best Paper Award} for ``Argumentation Models for Cyber Attribution". 

\item ``Systems and Methods for Data Driven Malware Task Identification"-- Selected for TechConnect
2016 Innovation Showcase.

\item Business Category - Most commercial potential winner (Idea: Weight Estimation from Anthropometric features), Medical Center of The Americas Foundation, 2014 (\$1000).

\item Graduate Scholarship to pursue M.S. at Syracuse University (2010 - 2012)
\end{itemize}
\section{\sc Academic Experience}
{\bf Arizona State University}, Tempe, Arizona USA\\
{\bf Graduate Research Assistant \href{http://cysis.engineering.asu.edu/}{(CySIS Lab)}} \hfill {\bf August, 2014 - present}\\
\textit{\underline{Tools:} Python, Spark, PostgreSQL, Prolog, tcpflow.}\\
\begin{enumerate}
	\item {\bf{Proactive Cyber-threat Intelligence}} 
	\begin{itemize}
		\item Developed an operational system for cyber threat intelligence gathering from darknet and deepnet sites. 
		
		\item The system employs data mining and machine learning techniques to collect information from hacker forum discussions and marketplaces offering products and services focusing on malicious hacking. 
		
		\item Currently, this system collects high-quality cyber threat warnings each week. These threat warnings include information on newly developed malware and exploits. 
		
		\item Developed data analysis tools to gather meaningful insights from this data to aid security experts for better threat analysis. 
		
		\item {\em Relevant publications:} [B-1, J-1, C-10, C-9, C-7]
	\end{itemize}
	
	
	\item {\bf{Reasoning framework for Cyber-attribution}} 
	\begin{itemize}
		\item Proposed a knowledge representation - machine learning (KR-ML) framework to reason about threat actors. 
		
		\item The framework combines an argumentation model based on DeLP (Defeasible Logic Programming) and machine learning classifiers to evaluate evidence and reason about actors responsible for an attack.
		
		\item The framework was evaluated by building a dataset from the capture-the-flag event held at DEFCON -- 10 million network attacks. 
		
		\item Achieved higher precision than previously reported approaches (evaluated on the same dataset) that rely on machine learning classifiers alone---a jump from 37\% to 64.5\%.
		
		\item {\em Relevant publications:} [B-2, J-3, C-3, C-5, C-6, C-8, BC-1]
		
	\end{itemize}
	
	
	\item {\bf{Malware task identification}} 
	\begin{itemize}
		\item Developed a novel cognitive learning model to identify tasks (e.g. logging keystrokes, recording video, establishing remote access, etc.) that the malware was designed to perform. 
		\item The proposed model was tested on different malware collections - including mutated and encrypted malware samples. 
		\item The model outperformed standard machine learning approaches in identifying the tasks.
		\item {\em Relevant publications:} [J-2, C-1, C-2, C-4]
	\end{itemize}
	

\end{enumerate}

{\bf Dartmouth College}, Hanover, New Hampshire USA\\
{\bf Research Associate \href{https://www.dartmouth.edu/~rhg/}{(Brain Engineering Lab)}} \hfill {\bf June, 2012 - July, 2014}\\
\textit{\underline{Tools:} MATLAB, C++, OpenCV.}
\begin{itemize}
	\item Learning representations for Object recognition and localization from image and video datasets using biologically inspired algorithms.
	\item Proposed a supervised object recognition algorithm that achieves corresponding classification rates in comparison with standard machine learning approaches - at a fraction of the time and space costs.
\end{itemize}
 

{\bf SUNY Upstate Medical University}, Syracuse, New York USA\\
{\bf Research Assistant} \hfill {\bf May, 2011 - June, 2012}\\
\textit{\underline{Tools:} MATLAB, C++.}\\
Registering Multi-Spectral Retinal images to find features and points of interest to estimate the abundance of Oxygen saturation in the blood vessels in retinal images to diagnose retinal disorders.

\section{\sc Patents}
\begin{itemize}[leftmargin =*]

\item ``Systems and Methods for Data Driven Malware Task Identification." \\U.S. Provisional Patent: 62/182,006, Submitted (Non-provisional), 2016. 

\item ``Intelligent darkweb crawling infrastructure for cyber threat intelligence collection."\\U.S. Provisional Patent: 62/409,291, Licensed by CYR3CON, 2016.
\end{itemize}


\section{\sc Publications}
{\bf *B} - {\em Book}, {\bf*J} - {\em Journal}, {\bf *C} - {\em Conference}, {\bf*BC} - {\em Book Chapter}\\

\begin{itemize}[leftmargin =*]

\item {[\bf B-2]}  {\bf E. Nunes}, P. Shakarian, G. Simari, A. Ruef ``Artificial Intelligence Tools for Cyber Attribution", {\em Under Preparation}, 2017. 

\item {[\bf B-1]} J. Robertson, A. Diab, E. Marin, {\bf E. Nunes}, V. Paliath, J. Shakarian, P. Shakarian ``Darkweb Cyber Threat Intelligence Mining", Cambridge University Press, 2017. 

\item {[\bf J-3]} {\bf E. Nunes}, P. Shakarian, G. Simari, A. Ruef ``Hybrid Structured Argumentation Models for Cyber Attribution: An Empirical Study on Identifying Threat Actors" {\em submitted (under review)}, 2017.

\item {[\bf J-2]} {\bf E. Nunes}, C. Buto, P. Shakarian, C. Lebiere, S. Bennati, R. Thomson ``Cognitively-Inspired Inference for Malware Task Identification" {\em submitted (under review)}, 2017.

\item {[\bf J-1]} J. Robertson, A. Diab, E. Marin, {\bf E. Nunes}, V. Paliath, J. Shakarian, P. Shakarian ``Darknet Mining and Game Theory for Enhanced Cyber Threat Intelligence" The Cyber Defense Review, 2016.

\item {[\bf C-10]} M. Almukaynizi, A. Grimm, {\bf E. Nunes}, J. Shakarian, P. Shakarian  ``Predicting Cyber Threats through User Connectivity in Darkweb and Deepweb Forums" ACM Computational Social Science (CSS), 2017.

\item {[\bf C-9]} M. Almukaynizi, {\bf E. Nunes}, K. Dharaiya, M. Senguttuvan, J. Shakarian, P. Shakarian  ``Proactive Identification of Exploits in the Wild Through Vulnerability Mentions Online" International Conference on Cyber Conflict (CyCon-US), 2017.


\item {[\bf C-8]} A. Ruef, {\bf E. Nunes}, G. Simari, P. Shakarian  ``Measuring Cyber Attribution In Games" IEEE APWG Symposium on Electronic Crime Research (eCrime), 2017.


\item {[\bf C-7]} {\bf E. Nunes}, A. Diab, A. Gunn, E. Marin, V. Mishra, V. Paliath, J. Robertson, J. Shakarian, A. Thart, P. Shakarian ``Darknet and Deepnet Mining for Proactive Cybersecurity Threat Intelligence" IEEE Conference on Intelligence and Security Informatics (ISI), 2016.

\item {[\bf C-6]} {\bf E. Nunes}, P. Shakarian, G. Simari, A. Ruef  ``Argumentation Models for Cyber Attribution"
IEEE/ACM International Symposium on Foundations of Open Source Intelligence and Security Informatics (FOSINT-SI), 2016 -- {\bf Best Paper Award}.

\item {[\bf C-5]} {\bf E. Nunes}, P. Shakarian, G. Simari ``Toward Argumentation-Based Cyber Attribution"
AAAI Workshop on Artificial Intelligence and Cyber security (AICS), 2016.

\item {[\bf BC-1]} {\bf E. Nunes}, N. Kulkarni, P. Shakarian, A Ruef, J. Little ``Cyber-Deception and Attribution in Capture-the-Flag Exercises" (extended version) in Cyber Deception: Building the Scientific Foundation (editors: S. Jajodia, V.S. Subrahmanian, V. Swarup, C. Wang) Springer, 2016.

\item {[\bf C-4]} {\bf E. Nunes}, C. Buto, P. Shakarian, C. Lebiere, S. Bennati, R. Thomson, H. Jaenisch ``Malware Task Identification: A Data Driven Approach"  IEEE/ACM International Symposium on Foundations of Open Source Intelligence and Security Informatics (FOSINT-SI), 2015.

\item {[\bf C-3]} {\bf E. Nunes},  N. Kulkarni, P. Shakarian, A Ruef, J. Little ``Cyber-Deception and Attribution in Capture-the-Flag Exercises"  IEEE/ACM International Symposium on Foundations of Open Source Intelligence and Security Informatics (FOSINT-SI), 2015.

\item {[\bf C-2]} C. Lebiere, S. Bennati, R. Thomson, P. Shakarian, {\bf E. Nunes}  ``Functional Cognitive Models of Malware Identification" 13th International Conference on Cognitive Modeling (ICCM), 2015.

\item {[\bf C-1]} R. Thomson, C. Lebiere, S. Bennati, P. Shakarian, {\bf E. Nunes}   ``Malware Identification Using Cognitively-Inspired Inference" 24th Conference on Behavior Representation in Modeling and Simulation (BRiMS), 2015.
   
\end{itemize}

\section{\sc Invited talks}
\begin{itemize}[leftmargin =*]

\item {\bf Cyber-Deception and Attribution in Capture-the-Flag Exercises}\\
The International Information System Security Certification Consortium (ISC2), Phoenix chapter, October, 2016.\\
Army Research Office's Cyber Deception Workshop, Washington, July 2015.

\item {\bf Automatic identification of malware tasks}\\
Cactus-Con, Tempe, Arizona, March, 2015.
\end{itemize}


\section{\sc Professional Experience}

{\bf Data Scientist}, \href{http://www.cyr3con.com/}{\bf Cyber Reconnaissance Inc. (CYR3CON)}  \hfill {\bf August, 2016 - Present}
\begin{itemize}
	\item Developed data analysis tools for threat intelligence to draw meaningful insights from data
	mined from darknet and deepnet markets /forums (including detection of 0-day exploits, identifying
	exploits targeting specific vulnerabilities, trend analytics in cyber threat landscape etc.)
	for customer specific requirements. In particular, built learning models for predicting likelihood of exploitation of a vulnerability,  named-entity recognition using RNN/LSTM seq2seq models.
	
	\item Consulted for SiteLock to improve their malicious web script detection model using machine learning techniques to make it more robust and less susceptible to false alarms
\end{itemize}



{\bf Security Automation Intern (Data Science)}, \href{https://www.paypal.com/us/home}{\bf PayPal}  \hfill {\bf May, 2017 - August, 2017}
\begin{itemize}
    \item Analyzed user login activity using Akamai logs and enriched it with other data feeds such as threat intelligence, merchant data, credential dumps.
	\item Implemented operational Anomaly detection models to detect Account Takeover (ATO) attacks to raise alerts for automated mitigation.  
	\item Visualized ATO attacks in real time on a dashboard in Splunk.
	
\end{itemize}


{\bf Research Consultant}, \href{http://www.cyr3con.com/}{\bf CYR3CON} (Client: \href{https://www.sitelock.com/}{\bf SiteLock})  \hfill {\bf June 2016 - August 2016}
\begin{itemize}
	\item Analyzed large dataset of malicious web scripts (PHP/HTML) to generate features indicative of malicious activity.
	\item Developed classification models to classify web scripts as malicious or not using the generated features in Python.
	\item Visualized the performance of the trained model overtime and analyzed the classification errors for further improvement through Plotly dashboard.
	\item {\bf Achieved malicious web script detection rate of $>$90\%.}
	
\end{itemize}

\section{\sc Technical Skills} 
\begin{itemize}[leftmargin =*]

\item {\bf Machine Learning:} Classification, regression, clustering, anomaly detection, feature engineering, online learning, Experience with deep learning.

\item{\bf Programming Languages:} Python, MATLAB, C++, Prolog, HTML, LaTeX. Familiar with C, PHP, LISP, R. 

\item{\bf Libraries:} scikit-learn, Weka, Pandas, OpenCV, Theano, Caffe. 

\item {\bf Databases:} SQL, PostgreSQL, MYSQL, Familiar with MongoDB.

\item {\bf Operating System:} Windows, Linux, Mac OS X. 

\item {\bf Tools:} Eclipse, MS Visual Studio, PyCharm. 

\item {\bf Big Data and Cloud:} Splunk, Familiar with Big Data Processing Platforms: Hadoop, Spark and Cloud tools: Amazon S3. 

\end{itemize}


\section{\sc Press}
\begin{itemize}[leftmargin=*]
\item \href{https://asunow.asu.edu/20160907-solutions-asu-researchers-hacking-hackers-new-approach}{Hacking the hackers}, ASU now: Access, Excellence, Impact. September 7, 2016.

\item \href{https://continuum.cisco.com/2016/08/18/arizona-state-builds-darknet-mining-model-finds-16-zero-days/}{Arizona State Builds Darknet Mining Model, Finds 16 Zero Days}, Cisco Continuum. August 18, 2016.

\item \href{https://www.helpnetsecurity.com/2016/08/10/cyber-threats-underground-markets/}{Over 300 new cyber threats pop up on underground markets each week}, HelpNetSecurity. August 10, 2016.

\item \href{http://www.forbes.com/sites/kevinmurnane/2016/08/08/machine-learning-goes-dark-and-deep-to-find-zero-day-exploits-before-day-zero/#49b6e2706d76}{ Machine Learning Goes Dark And Deep To Find Zero-Day Exploits Before Day Zero}, Forbes. August 8, 2016.

\item \href{https://www.technologyreview.com/s/602115/machine-learning-algorithm-combs-the-darknet-for-zero-day-exploits-and-finds-them/}{ Machine-Learning Algorithm Combs the Darknet for Zero Day Exploits, and Finds Them},
MIT Tech Review. August 5, 2016. ACM TechNews. August 5, 2016.

\end{itemize}

\section{\sc Service}
{\bf Journal Reviewer:}
\begin{itemize}
	\item Social Network Analysis and Mining (SNAM), 2017.
	\item Sustainability, 2017. 
\end{itemize}

{\bf Conference Reviewer:}
\begin{itemize}
\item ACM SIGKDD Conferences on Knowledge Discovery and Data Mining (KDD), 2015, 2016.
\item AAAI Conference on Artificial Intelligence (AAAI), 2016.
\item International Conference on Autonomous Agents and Multiagent Systems, 2015. 
\end{itemize}


\section{\sc References} Available on request

\end{resume}
\end{document}




